### 2019-05-06 Thesis/games.tex
Did some things.

@@

An examination of the definitions tells us that
\begin{proposition}
  Let $A_i,B$ be games and let $\phi_i$ be tree embeddings from $A_i$ to $B$.  
  Then $\langle \zz_{\phi_i} \rangle = \zz_\phi$, where $\phi$ is the tree embeddings from $\prod_iA_i$ to $B$ given by
  \[
    \phi(s) = \begin{cases}
      \epsilon & \text{if $s=\epsilon$} \\
      \phi_i(s\vert_{A_i}) & \text{if $s$ starts with a move from $A_i$}
    \end{cases}
    \]
  \label{PropProductOfTreeEmbeddings}
\end{proposition}
\begin{proof}
  The only thing we really need to check is that this is indeed a tree embedding.  
  Let $sb,sc$ be positions in $\prod_iA_i$, where $b,c$ are $P$-moves.
  Then $sb,sc$ must start with the same move, so if $\phi(sb)=\phi(sc)$ then we have $\phi_i(sb)=\phi_i(sc)$ for some $i$ and therefore $b=c$.
\end{proof}

Note that $\langle\sigma_i\rangle$ is not in general innocent, even if all the $\sigma_i$ are, and there is no version of Proposition \ref{PropProductOfTreeEmbeddings} that works for subset inclusion strategies.
Of course, since a subset inclusion is a special case of a tree embedding, then $\langle \subs_i\rangle$ is always a tree embedding strategy.

@@

\section{Tree Embeddings and Zigzag Strategies}

We can generalize the subset inclusions of the previous chapter to \emph{tree embeddings}.  
Tree embeddings are similar to subset inclusions, but generated by a function between plays, rather than between moves.  
A consequence of this is that while tree embeddings do give rise to strategies, these strategies are not in general innocent.

\begin{definition}
  Let $A,B$ be games.  
  A \emph{tree embedding} from $A$ to $B$ is a function $\phi\from P_A \hookrightarrow P_B$ such that
  \begin{itemize}
    \item $\phi$ preserves length and justification indices; 
    \item for all sequences $s,t\in P_A$, if $t\prefix s$ then $\phi(t)\prefix\phi(s)$; and
    \item if $\phi(sb)=\phi(sc)$, where $b,c$ are $P$-moves in $A$, then $b=c$.
  \end{itemize}

  Given a tree embedding $\phi$ from $A$ to $B$, we define a strategy $\zz_\phi\from B \implies A$ by
  \[
    \zz_\phi = \{s\in P_{B\implies A}\suchthat\text{for all even-length $t\prefix s$, $t\vert_B=\phi(t\vert_A)$}\}\,.
    \]
\end{definition}
\begin{example}
  If $i$ is a subset inclusion from $A$ to $B$, then $i_*$ is a tree embedding from $A$ to $B$ and $\zz_{i_*}=\subs_i$.
\end{example}

\begin{definition}
  Given a tree embedding from $A$ to $B$, and a play $s\in P_{C\implies A}$ for some $C$, we write $s^\phi$ for the play obtained by replacing the moves of $s\vert_A$ wholesale with the moves of $\phi(s\vert_A)$ (using the fact that $\phi$ preserves length and justification indices).
\end{definition}

  In particular, if $\phi$ is a tree embedding from $A$ to $B$ and $\psi$ is a tree embedding from $B$ to $C$, then $\psi\circ\phi$ is a tree embedding from $A$ to $C$ and $\zz_{\psi\circ\phi}=\zz_\psi;\zz_\phi$.
  \label{PropTree}
\end{proposition}
\begin{proof}
  Suppose that $\s\in\sigma\|\zz_\phi$.  
  Then $\s\vert_{C,B}\in\sigma$ and $t\vert_B=\phi(t\vert_A)$ for all even-length $t\prefix \s\vert_{B,A}$.  
  Then it is clear that $(\s\vert_{C,A})^\phi=\s\vert_{C,B}$.

\begin{definition}
  We say that a tree embedding $\phi$ is a \emph{tree isomorphism} if it is a bijection.
\end{definition}

@@

\begin{proposition}
  $\G$ is a distributive sequoidal category.
\end{proposition}
\begin{proof}
  Let $(A_i),X$ be games.
  By Proposition \ref{PropProductOfTreeEmbeddings}, the morphism $\langle \pr_i\sequoid X\rangle$ is given by the tree embedding $\phi\from P_{\prod_i(A_i\sequoid X)}\to P_{\prod_iA_i\sequoid X}$ defined as follows.
  \[
    \phi(s) = \begin{cases}
      \epsilon & \text{if $s=\epsilon$} \\
      [\inj_{A_j},\inj_{X}]_*(s) & \text{if $s$ begins with a move in the $j$-th component}
    \end{cases}
    \]
  When we say $[\inj_{A_j},\inj_{X^j}]_*(s)$, we have considered $s$ as a sequence in $(M_{A_j} + M_{X^j})^*$.

@@

\begin{proposition}
  $\G$ is a strongly distributive sequoidal category.
\end{proposition}
\begin{proof}
  By Proposition \ref{PropProductOfTreeEmbeddings}, the morphism $\langle (A_1\sequoid(\cdots\sequoid(A_n \sequoid\pr_i)\cdots))\rangle$ is given by the tree embedding 
  \[
    \phi\from P_{\prod_i (A_1 \sequoid(\cdots\sequoid(A_n\sequoid B_i)\cdots))} \to P_{A_1\sequoid(\cdots\sequoid(A_n\sequoid \prod_iB_i))}
    \]
  defined as follows.
  \[
    \phi(s) = \begin{cases}
      \epsilon & \text{if $s=\epsilon$} \\
      [\inj_{A_1,\cdots,A_n},\inj_{B_j}]_*(s) & \parbox[t][][t]{180pt}{if $s$ begins with a move in the $j$-th component}
    \end{cases}
    \]
  Note that $\phi$ is not in general injective, since if $s$ occurs entirely inside one of the copies of the $A_i$, then $\phi(s)=\phi(s')$ for any identical sequence $s'$ occurring inside one of the other copies of the $A_i$.

@@

\begin{proposition}
  $\G$ is a decomposable sequoidal category.
\end{proposition}
\begin{proof}
  Let $A,B$ be games.  
  By Proposition \ref{PropProductOfTreeEmbeddings}, the strategy 
  \[
    \langle \wk_{A,B},\sym_{A,B};\wk_{A,B}\rangle
    \]
  is given by the tree embedding $\phi$ from $(A \sequoid B) \times (B \sequoid A)$ to $A \tensor B)$ given by
  \[
    \phi(s) = \begin{cases}
      \epsilon & \text{if $s=\epsilon$} \\
      s\vert_{A \sequoid B} & \text{if $s$ takes place entirely within $A\sequoid B$} \\
      s\vert_{B \sequoid A} & \text{if $s$ takes place entirely within $B\sequoid A$}
    \end{cases}\,.
    \]
  We claim that this tree embedding is a bijection.  
  Indeed, it is certainly injective.
  Now let $s\in P_{A\tensor B}$ be a non-empty play.  
  Then, if $s$ begins with a move in $A$, we have $s=\phi((\inj_{A\sequoid B})_*(s))$, and if $s$ begins with a move in $B$, we have $s=\phi((\inj_{B\sequoid A})_*(s)$.  
  Therefore, $\phi$ is a tree isomorphism, so $\dec_{A,B}=\zz_\phi$ is an isomorphism in $\G$.

@@

  The morphism in question is the (non-innocent) zigzag strategy given by the tree embedding $\phi_n\from P_{A^{\sequoid n}}\to P_{\oc A}$ defined by
  \[
    \phi_n(s) = \nabla_*(s)\,,
    \]
  where $\nabla\from M_A+\cdots + M_A$ is the co-diagonal.

@@

\section{Arena-only Semantics}

>>>>

\section{Tree Immersions and Zigzag Strategies}

We can generalize the subset inclusions of the previous chapter to \emph{tree immersions}.  
Tree immersions are similar to subset inclusions, but generated by a function between plays, rather than between moves.  
A consequence of this is that while tree immersions do give rise to strategies, these strategies are not in general innocent.

\begin{definition}
  Let $A,B$ be games.  
  A \emph{tree immersion} from $A$ to $B$ is a function $\phi\from P_A \hookrightarrow P_B$ such that
  \begin{itemize}
    \item $\phi$ preserves length and justification indices; 
    \item for all sequences $s,t\in P_A$, if $t\prefix s$ then $\phi(t)\prefix\phi(s)$; and
    \item if $\phi(sb)=\phi(sc)$, where $b,c$ are $P$-moves in $A$, then $b=c$.
  \end{itemize}

  Given a tree immersion $\phi$ from $A$ to $B$, we define a strategy $\zz_\phi\from B \implies A$ by
  \[
    \zz_\phi = \{s\in P_{B\implies A}\suchthat\text{for all even-length $t\prefix s$, $t\vert_B=\phi(t\vert_A)$}\}\,.
    \]
\end{definition}
\begin{example}
  If $i$ is a subset inclusion from $A$ to $B$, then $i_*$ is a tree immersion from $A$ to $B$ and $\zz_{i_*}=\subs_i$.
\end{example}

\begin{definition}
  Given a tree immersion from $A$ to $B$, and a play $s\in P_{C\implies A}$ for some $C$, we write $s^\phi$ for the play obtained by replacing the moves of $s\vert_A$ wholesale with the moves of $\phi(s\vert_A)$ (using the fact that $\phi$ preserves length and justification indices).
\end{definition}

  In particular, if $\phi$ is a tree immersion from $A$ to $B$ and $\psi$ is a tree immersion from $B$ to $C$, then $\psi\circ\phi$ is a tree immersion from $A$ to $C$ and $\zz_{\psi\circ\phi}=\zz_\psi;\zz_\phi$.
  \label{PropTree}
\end{proposition}
\begin{proof}
  Suppose that $\s\in\sigma\|\zz_\phi$.  
  Then $\s\vert_{C,B}\in\sigma$ and $t\vert_B=\phi(t\vert_A)$ for all even-length $t\prefix \s\vert_{B,A}$.  
  Then it is clear that $(\s\vert_{C,A})^\phi=\s\vert_{C,B}$.

\begin{definition}
  We say that a tree immersion $\phi$ is a \emph{tree isomorphism} if it is a bijection.
\end{definition}

@@

An examination of the definitions tells us that
\begin{proposition}
  Let $A_i,B$ be games and let $\phi_i$ be tree immersions from $A_i$ to $B$.  
  Then $\langle \zz_{\phi_i} \rangle = \zz_\phi$, where $\phi$ is the tree immersion from $\prod_iA_i$ to $B$ given by
  \[
    \phi(s) = \begin{cases}
      \epsilon & \text{if $s=\epsilon$} \\
      \phi_i(s\vert_{A_i}) & \text{if $s$ starts with a move from $A_i$}
    \end{cases}
    \]
  \label{PropProductOfTreeEmbeddings}
\end{proposition}
\begin{proof}
  The only thing we really need to check is that this is indeed a tree immersion.  
  Let $sb,sc$ be positions in $\prod_iA_i$, where $b,c$ are $P$-moves.
  Then $sb,sc$ must start with the same move, so if $\phi(sb)=\phi(sc)$ then we have $\phi_i(sb)=\phi_i(sc)$ for some $i$ and therefore $b=c$.
\end{proof}

Note that $\langle\sigma_i\rangle$ is not in general innocent, even if all the $\sigma_i$ are, and there is no version of Proposition \ref{PropProductOfTreeEmbeddings} that works for subset inclusion strategies.
Of course, since a subset inclusion is a special case of a tree immersion, then $\langle \subs_i\rangle$ is always a tree immersion strategy.

@@

@@

\begin{proposition}
  $\G$ is a distributive sequoidal category.
\end{proposition}
\begin{proof}
  Let $(A_i),X$ be games.
  By Proposition \ref{PropProductOfTreeEmbeddings}, the morphism $\langle \pr_i\sequoid X\rangle$ is given by the tree immersion $\phi\from P_{\prod_i(A_i\sequoid X)}\to P_{\prod_iA_i\sequoid X}$ defined as follows.
  \[
    \phi(s) = \begin{cases}
      \epsilon & \text{if $s=\epsilon$} \\
      [\inj_{A_j},\inj_{X}]_*(s) & \text{if $s$ begins with a move in the $j$-th component}
    \end{cases}
    \]
  When we say $[\inj_{A_j},\inj_{X^j}]_*(s)$, we have considered $s$ as a sequence in $(M_{A_j} + M_{X^j})^*$.

@@

\begin{proposition}
  $\G$ is a strongly distributive sequoidal category.
\end{proposition}
\begin{proof}
  By Proposition \ref{PropProductOfTreeEmbeddings}, the morphism $\langle (A_1\sequoid(\cdots\sequoid(A_n \sequoid\pr_i)\cdots))\rangle$ is given by the tree immersion 
  \[
    \phi\from P_{\prod_i (A_1 \sequoid(\cdots\sequoid(A_n\sequoid B_i)\cdots))} \to P_{A_1\sequoid(\cdots\sequoid(A_n\sequoid \prod_iB_i))}
    \]
  defined as follows.
  \[
    \phi(s) = \begin{cases}
      \epsilon & \text{if $s=\epsilon$} \\
      [\inj_{A_1,\cdots,A_n},\inj_{B_j}]_*(s) & \parbox[t][][t]{180pt}{if $s$ begins with a move in the $j$-th component}
    \end{cases}
    \]
  Note that $\phi$ is not in general injective, since if $s$ occurs entirely inside one of the copies of the $A_i$, then $\phi(s)=\phi(s')$ for any identical sequence $s'$ occurring inside one of the other copies of the $A_i$.

@@

\begin{proposition}
  $\G$ is a decomposable sequoidal category.
\end{proposition}
\begin{proof}
  Let $A,B$ be games.  
  By Proposition \ref{PropProductOfTreeEmbeddings}, the strategy 
  \[
    \langle \wk_{A,B},\sym_{A,B};\wk_{A,B}\rangle
    \]
  is given by the tree immersion $\phi$ from $(A \sequoid B) \times (B \sequoid A)$ to $A \tensor B)$ given by
  \[
    \phi(s) = \begin{cases}
      \epsilon & \text{if $s=\epsilon$} \\
      s\vert_{A \sequoid B} & \text{if $s$ takes place entirely within $A\sequoid B$} \\
      s\vert_{B \sequoid A} & \text{if $s$ takes place entirely within $B\sequoid A$}
    \end{cases}\,.
    \]
  We claim that this tree immersion is a bijection.  
  Indeed, it is certainly injective.
  Now let $s\in P_{A\tensor B}$ be a non-empty play.  
  Then, if $s$ begins with a move in $A$, we have $s=\phi((\inj_{A\sequoid B})_*(s))$, and if $s$ begins with a move in $B$, we have $s=\phi((\inj_{B\sequoid A})_*(s)$.  
  Therefore, $\phi$ is a tree isomorphism, so $\dec_{A,B}=\zz_\phi$ is an isomorphism in $\G$.

@@

  The morphism in question is the (non-innocent) zigzag strategy given by the tree immersion $\phi_n\from P_{A^{\sequoid n}}\to P_{\oc A}$ defined by
  \[
    \phi_n(s) = \nabla_*(s)\,,
    \]
  where $\nabla\from M_A+\cdots + M_A$ is the co-diagonal.

@@

\section{Arena-only Semantics}
\label{SecArenaOnly}

### 2019-05-06 Thesis/pmonads2.tex
Did some things.

\begin{definition}
  Given a set $X$ and a \Mellies morphism $\sigma \from 1 \to (X \to \bC)$, we say that $\sigma$ \emph{accepts} a sequence $u\in X^*$ if $\sigma;\xi_u\ne\bot$.
  We write $\Acc(\sigma)$ for the set of all sequences accepted by $\sigma$.
\end{definition}

@@

\begin{proposition}
  Let $\sigma\from 1 \to (j(p) \to \bC)$, $\tau\from 1 \to (j(q) \to \bC)$ be two representatives of the same morphism $1 \to \bC$ in $\G/\oppcat\X$.  
  Then $(p,\Acc(\sigma))$ and $(q,\Acc(\tau))$ are equivalent.
  \label{PropAccEquivalent}
\end{proposition}
\begin{proof}
  Since the relation on pairs $(p,\U)$ is an equivalence relation, it suffices to assume that $\sigma$ and $\tau$ are related by the relation that generates the equivalence relation on \Mellies morphisms; i.e., that there is a morphism $f\from p \to q$ such that $\sigma = \tau;(j(f)\to \bC)$.

  Let $u\in j(p)^*$.  
  Then we have
  \begin{IEEEeqnarray*}{rCl}
    u\in\Acc(\sigma) & \Leftrightarrow & \sigma;\xi_u\ne\bot \\
    & \Leftrightarrow & \tau;(j(f)\to\bC);\xi_u\ne\bot \\
    & \Leftrightarrow & \tau;\xi_{j(f)_*u}\ne\bot \\
    & \Leftrightarrow & j(f)_*u \in \Acc(\tau)\,.
  \end{IEEEeqnarray*}
  Therefore, $(p,\Acc(\sigma))$ and $(q,\Acc(\tau))$ are equivalent.
\end{proof}

@@

  Then we define $\bP(\sigma\downarrow)$ to be
  \[
    \bP(V, \Acc(\sigma)\,.
    \]
  \label{DefProbNonBot}
\end{definition}

@@

>>>>

\begin{definition}
  Given a set $X$ and a \Mellies morphism $\sigma \from 1 \to (X \to \bC)$, we say that $\sigma$ \emph{accepts} a sequence $u\in X^*$ if $\sigma;\xi_u\ne\bot$.
  We write $\Acc(\sigma)$ for the set of all sequences accepted by $\sigma$.

  More generally, if $\sigma\from 1 \to (X \to A)$ is a \Mellies morphism and $\tau\from 1 \to A$ is an ordinary morphism in $\G$, we write
  \[
    \Acc_\tau(\sigma) = \{u\in X^*\suchthat \sigma;\xi_u = \tau\}\,.
    \]
  When $A=\bC$, we have $\Acc(\sigma) = \Acc_{\deno{\skipp}}(\sigma)$.
  \label{DefAcc}
\end{definition}

@@

\begin{proposition}
  Let $\sigma\from 1 \to (j(p) \to A)$, $\sigma'\from 1 \to (j(q) \to A)$ be two representatives of the same morphism $1 \to A$ in $\G/\oppcat\X$.  
  Let $\tau\from 1 \to A$ be an ordinary morphism in $\G$.
  Then $(p,\Acc_\tau(\sigma))$ and $(q,\Acc_\tau(\sigma'))$ are equivalent.
  In particular, if $A=\bC$, then $(p,\Acc(\sigma))$ and $(q,\Acc(\sigma')$ are equivalent.
  \label{PropAccEquivalent}
\end{proposition}
\begin{proof}
  Since the relation on pairs $(p,\U)$ is an equivalence relation, it suffices to assume that $\sigma$ and $\sigma'$ are related by the relation that generates the equivalence relation on \Mellies morphisms; i.e., that there is a morphism $f\from p \to q$ such that $\sigma = \sigma';(j(f)\to \bC)$.

  Let $u\in j(p)^*$.  
  Then we have
  \begin{IEEEeqnarray*}{rCl}
    u\in\Acc_\tau(\sigma) & \Leftrightarrow & \sigma;\xi_u=\tau \\
    & \Leftrightarrow & \sigma';(j(f)\to A);\xi_u=\tau \\
    & \Leftrightarrow & \sigma';\xi_{j(f)_*u}=\tau \\
    & \Leftrightarrow & j(f)_*u \in \Acc_\tau(\sigma')\,.
  \end{IEEEeqnarray*}
  Therefore, $(p,\Acc_\tau(\sigma))$ and $(q,\Acc_\tau(\sigma'))$ are equivalent.
\end{proof}

@@

  Then we define $\bP(\sigma\downarrow)$ to be
  \[
    \bP(V, \Acc(\sigma))\,.
    \]
  \label{DefProbNonBot}
\end{definition}

@@

Perhaps a better way of thinking about the difference between the two models, then, is to consider what the denotation of a term actually looks like.  
In the language IA${}_\bB$, we can define a term that converges to $\true$ with probability $\frac23$ and to $\false$ with probability $\frac13$ by
\[
  \Y_\bool(\lambda b.\If \choose_{\frac12} \Then \true \Else (\If \choose_{\frac12} \Then b \Else \false))\,.
  \]
Here, we have renamed $\ask_{\bB}$ to $\choose_{\frac12}$ to give a better idea of what the term does in the probabilistic setup.

Now the denotation of this term in $\Kl_{R_{\bB}}\G$ is given by the denotation of the term-in-context
\[
  c\from\bool\ts\Y_{\bool}(\lambda b.\If c \Then \true \Else (\If c \Then b \Else \false))
  \]
in $\G$.
If $\G$ is the category of games, then this morphism is the strategy with maximal plays taking one of the following two forms.
\begin{mathpar}
  q(q\false q\true)^nq\true \true
  \and
  q(q\false q\true)^nq\false q\false\false
\end{mathpar}
In other words, it is not at all clear from the denotation that the term should give $\true$ with probability $\frac23$ and $\false$ with probability $\frac13$.

In $\G/\Rv_{\Omega}^{FS}$, however, we can model a term that has the same behaviour using the morphism
\[
  \left(V_{\frac23}, \id_\bB\right)\,,
  \]
which makes it much clearer what the probabilistic behaviour is.

\section{The Probabilistic Equivalence Relation on Morphisms}

\begin{definition}
  Let $A$ be an object of $\G$.  
  Let $(V\from\Omega \to X,\sigma\from X \to A)$ be a morphim $1\to A$ in $\G/\oppcat{(\Rv_{\Omega}^{FS})}$, and let $\tau \from 1 \to A$ be a morphism in $\G$.  
  Recall from \ref{DefAcc} the definition
  \[
    \Acc_\tau(\sigma) = \{u\in X^* \suchthat \sigma;\xi_u = \tau\}\,.
    \]
  Now we define
  \[
    \bP(\sigma = \tau)
    \]
  to be
  \[
    \bP(V,\Acc_\tau(\sigma))\,.
    \]
  Given Kleisli morphisms $\sigma,\tau\from 1 \to A$, we say that $\sigma\approx_{\bP}\sigma'$ if for all $\tau\from 1 \to A$, we have
  \[
    \bP(\sigma = \tau) = \bP(\sigma' = \tau)\,.
    \]
  \label{DefProbEquiv}
\end{definition}
\begin{remark}
  In the case that $A=\bC$, we have $\Acc(\sigma) = \Acc_{\deno{\skipp}}(\sigma)$ and
  \[
    \bP(\sigma\converges) = \bP(\sigma = \deno{\skipp}) = 1 - \bP(\sigma = \bot)\,.
    \]
  Then $\sigma\approx_{\bP}\sigma'$ if and only if $\bP(\sigma\converges)=\bP(\sigma'\converges)$.
\end{remark}

\begin{proposition}
  i) Definition \ref{DefProbEquiv} is well defined.  
  I.e., let
  \begin{mathpar}
    (V\from\Omega \to X,\sigma\from 1 \to (X \to A))
    \and
    (W\from\Omega \to Y,\sigma'\from 1 \to (Y \to A))
  \end{mathpar}
  be representatives for the same morphism in $\G/\Rv_{\Omega}^{FS}$, and let $\tau \from 1 \to A$ be an ordinary morphism in $\G$.  
  Then $\bP(\sigma = \tau) = \bP(\sigma' = \tau)$.  
\end{proposition}
\begin{proof}
  By Proposition \ref{PropAccEquivalent}, $(V,\Acc_\tau(\sigma))$ and $(W,\Acc_\tau(\sigma'))$ are equivalent pairs, and therefore, by Proposition \ref{PropProbabilityWellDefined}, $\bP(\sigma = \tau) = \bP(\sigma' = \tau)$.
\end{proof}

\section{Danos-Harmer Probabilistic Game Semantics}

We really want to show that the equivalence relation $\approx_{\bP}$ respects composition of morphisms, but this does not seem to be possible in the general setting.  
Accordingly, we pass now to the special case when $\G$ is the category of games and strategies.  
More specifically, we shall use the arena-only semantics which we developed in \sec\ref{SecArenaOnly} -- so the objects of our category $\G$ will be arenas and the morphisms will be single-threaded strategies between arenas.

\begin{definition}
  Let $\sigma,\sigma'$ be strategies $A \to B$.  
  We say that $\sigma\approx_\bP\sigma'$ if $\Lambda(\sigma)\approx_{\bP}\Lambda(\sigma')$ as strategies $1 \to (A \to B)$.
\end{definition}

\begin{definition}
  Let $X$ be a set and let $u\in X^*$ be a sequence.  
  Consider $X$ as an arena $\ul X$.  
  Then we write $qu$ for the play in $\ul X$ given by
  \[
    q\,u^{(1)}\,\cdots\,q\,u^{(|u|-1)}\,.
    \]
\end{definition}

\begin{proposition}
  Let $X$ be a set, considered as an arena, and let $\sigma \from X \to A$ be a single-threaded strategy.
  Let $\tau$ be a single-threaded strategy for $A$.  
  Then, if $u\in X^*$ is a sequence, we have $u\in\Acc_\tau(\sigma)$ if and only if
  \[
    \{s\vert_A \suchthat s\in\sigma;\,s\vert_{\ul X} = qu\} = \tau\,.
    \]
\end{proposition}
\begin{proof}
  Immediate from the definition of composition and from our description of the strategy $\xi_u$.
\end{proof}

\begin{definition}
  Recall that we have written $s\vert_A$ for the restriction of a sequence in a compound game to the moves occurring in some constituent part $A$, and similarly for a list $s\vert_{A_1,\cdots,A_n}$.
  If $s$ is a sequence in an arena of the form $\ul{X\times Y}$; i.e., the arena in which player $O$ has an initial move $q$ to which player $P$ replies with some pair $(x,y)\in X\times Y$, the we write $s\vert_X$ for the play formed by projecting every such pair $(x,y)$ on to its first component $x$.
\end{definition}

\begin{lemma}
  Let $\sigma\from A \to (\ul{X} \to B)$, $\tau \from B \to (\ul{Y} \to C)$ be strategies, where $X,Y$ are sets.
  Write $\sigma\semicom_{\text{Mell}}\tau \from A \to (\ul{X\times Y} \to C)$ for the \Mellies composition of $\sigma$ and $\tau$.

  Let $s\in\sigma\semicom_{\text{Mell}}\tau$.  
  Then there exist four sequence $s_X,s_Y,\s_X,\s_Y$ such that
  \begin{itemize}
    \item $s$ is an interleaving of the sequences $s_X$ and $s_Y$;
    \item $\s_X\in\sigma$ and $\s_Y\in\tau$;
    \item $s_X\vert_{A,X} = \s_X\vert_{A,X}$; and
    \item $s_Y\vert_{C,Y} = \s_Y\vert_{C,Y}$.
  \end{itemize}
  \label{LemMelliesDecomposition}
\end{lemma}
\begin{proof}
  Recall that $\sigma\semicom_{\text{Mell}}\tau$ is given by the following composite in $\G$, where $\mu$ is the composite $\langle\ul{\pr_X},\ul{\pr_Y}\rangle$.
  \[
    A \xrightarrow{\sigma}
    (\ul{X} \to B) \xrightarrow{\ul{X} \to \tau}
    (\ul X \to (\ul Y \to C)) \to
    ((\ul X \times \ul Y) \to C) \xrightarrow{\mu\to C}
    (\ul{X\times Y} \to C)
    \]
  We consider the composite of the first two morphisms.  
  We know that a play $t\in \sigma;(\X\to \tau)$ is given by $\s\vert_{A,X,Y,C}$, where $\s\vert_{A,X,B}\in\sigma$ and $\s\vert_{B,Y,C}\in\tau$.
  Write $\s_X$ for $\s\vert_{A,X,B}$ and $\s_Y$ for $\s\vert_{B,Y,C}$.

  Now suppose that $s$ is a sequence in the whole composition, and let
  \[
    \t\in ((A\times\mu);\cong)\|((\sigma\times \ul Y);\tau)
    \]
  be such that $\t\vert_{A,\ul{X \times Y}\to C}=s$.
  Write $t=\t\vert_{A,\ul X \to (\ul Y \to C)}\in\sigma;(\ul X \to \tau)$ and let $\s$ cover $t$ as above.
  Then $\t$ is formed from $t$ by inserting between every pair $q\,x$ of moves in $\ul X$ a pair $q\,(x,y_0)$ in $\ul{X\times Y}$ for some $y_0$, and between every pair $q\,y$ of moves in $\ul Y$ a pair $q\,(x_0,y)$ in $\ul{X \times Y}$ for some $x_0$.
  This gives a partitition of $s\vert_{\ul {X \times Y}}$ into moves that occur before a move in $\ul X$ and moves that occur before a move in $\ul Y$ in the sequence $\t$.
  We then define $s_X$ to be the sequence formed from $\s_X\vert_A$, together with those moves in $\ul{X \times Y}$ that occur before a move in $\ul X$ in $\t$, and $s_Y$ fto be formed from $\s_Y\vert_C$, together with those moves in $\ul{X\times Y}$ that occur before a move in $\ul Y$ in $\t$.

  Then we have $s_X\vert_{A,X}=\s_X\vert_{A,X}$ and $s_Y\vert_{C,Y} = \s_Y\vert_{C,Y}$ as desired.
\end{proof}

\begin{proposition}
  Let $\sigma,\sigma'\from A \to B$ and $\tau,\tau'\from B \to C$ be morphisms in $\G/\Rv_{\Omega}^{FS}$, where $\G$ is the category of games and single-threaded strategies.
  If $\sigma\approx_{\bP}\sigma'$ and $\tau\approx_\bP\tau'$, then $\sigma;\tau\approx_\bP\sigma';\tau'$.
\end{proposition}
\begin{proof}
  Suppose that $\sigma$ is given by a single-threaded strategy $A \to (\ul X \to B)$ and $\tau$ by a single-threaded strategy $B \to (\ul Y \to C)$.

  Suppose $s\in\sigma;\tau$ satisfies $s\vert_{\ul{X\times Y}}=qu$, for some sequence $u\in(X\times Y)^*$.
  By Lemma \ref{LemMelliesDecomposition}, $s$ can be decomposed into sequences $s_X$ and $s_Y$ such that there are $\s_X\in\sigma$ and $\s_Y\in\tau$ with $\s_X\vert_{X,A}=s\vert_{X,A}$ and $\s_Y\vert_{Y,C}=s_Y\vert_{Y,C}$.
  We have $\s_X\vert_X=qv$ and $\s_Y\vert_Y=qw$ for sequences $v\in X^*$ and $w\in Y^*$, and $s_X\vert_{X\times Y} = qV$ and $s_Y\vert_{X\times Y}=qW$ for sequences $V\in (X\times Y)^*,W\in (X\times Y)^*$ such that $(\pr_X)_*V = v$ and $(\pr_Y)_*W = w$, and such that $u$ is an interleaving of $V$ and $W$.

  Now write $\hat\sigma$ for $\sigma;\xi_v$ and $\hat\tau$ for $\tau;\xi_w$.
  We claim that $(\sigma;\tau);\xi_u = \hat{\sigma};\hat{\tau}$.

  Thus, $\sigma$ and $\tau$ give rise to maps
  \begin{mathpar}
    \phi_{\sigma,\tau}\from (X\times Y)^* \to X^* \times Y^*
    \and
    \Phi_{\sigma,\tau}\from (X\times Y)^* \to (X\times Y)^* \times (X \times Y)^*
  \end{mathpar}
  (sending $u$ to $(v,w)$ and to $(V,W)$ respectively), such that the components of $\Phi(u)$ form a decomposition of $u$, and such that $\phi(u) = ((\pr_X)_*\times(\pr_Y)_*)(\Phi(u))$.
\end{proof}
